\subsection{Mechanical Testing}

To ensure maximum reliability, safety, and performance, Kamikaze’s mechanical system underwent a comprehensive and rigorous testing process. This approach ensured seamless operation under challenging underwater conditions, minimized the risk of failure, and upheld high safety standards.

\hspace{10pt} From the initial design phase, all components were carefully developed with a strong focus on safety, integration, and effectiveness. Before moving on to the final design and manufacturing stage, every prototype was thoroughly tested and refined to ensure flawless incorporation into Kamikaze’s final structure.

\vspace{-0.5\baselineskip}
\begin{itemize}
    \setlength{\itemsep}{0pt}
    \item \textbf{Pneumatic System Testing:} To ensure the reliability and performance of the pneumatic manipulators, a series of targeted tests were conducted. All pneumatic hoses, joints, and fittings were visually inspected to ensure proper assembly and tight sealing. The system was then pressurized, and any air leakage was detected by listening to hissing sounds particularly at fittings and connectors. Any issues were promptly resolved to ensure leak-free, efficient pneumatic actuation.
    \item \textbf{Sealing Mechanism Testing:} The electronic enclosure's sealing was tested under pressure conditions similar to those expected during operation. The enclosure was submerged and weighed underwater to check for any water ingress. If a leak was observed, compressed air was introduced into the enclosure, and the source of the leakage was identified by monitoring escaping bubbles. This allowed for targeted repairs and ensured complete waterproofing.
\end{itemize}

These mechanical and functional tests were complemented by a structured troubleshooting methodology, including:

\vspace{-0.5\baselineskip}
\begin{itemize}
    \setlength{\itemsep}{0pt}
    \item Component isolation to identify faulty subsystems.
    \item Visual inspections and real-time monitoring during tests.
    \item Failure mode analysis to understand and mitigate risks.
\end{itemize}