\subsection{Project Management}

\subsubsection{Project Scheduling}

The vehicle development schedule has four phases (Further illustrated in Appendix \ref{app:project_plan}):

\vspace{-0.5\baselineskip}
\begin{enumerate}[leftmargin=0pt, itemindent=20pt]
    \setlength{\itemsep}{0pt} 
    \item \textbf{Training Phase (12 weeks, Aug 1 - Oct 16, 2024)}
    
    \vspace{-0.5\baselineskip}
    \begin{itemize}[leftmargin=0pt, itemindent=20pt]
        \setlength{\itemsep}{0pt} 
        \item Foundational and specialized training in software, mechanical, and electrical systems.
        \item ROV-specific training, task automation, and mock challenges.
    \end{itemize}
    \item \textbf{Planning Phase (2 weeks, Oct 17 - Oct 31, 2024)}
    \vspace{-0.8cm}
    \begin{itemize}[leftmargin=0pt, itemindent=20pt]
        \setlength{\itemsep}{0pt}
        \item Finalize designs, select components, and define software and electrical frameworks.
    \end{itemize}
    \item \textbf{Prototype Build \& Testing (19 weeks, Nov 1, 2024 - Mar 14, 2025)}
    \vspace{-0.5\baselineskip}
    \begin{itemize}[leftmargin=0pt, itemindent=20pt]
        \setlength{\itemsep}{0pt} 
        \item Mechanical assembly, electrical integration, and software implementation.
        \item Underwater testing, and system integration.
    \end{itemize}
    \item \textbf{Final Preparation \& Mock Competitions (Mar 14 - Apr 24, 2025)}
    
    \vspace{-0.5\baselineskip}
    \begin{itemize}[leftmargin=0pt, itemindent=20pt]
        \setlength{\itemsep}{0pt} 
        \item Simulate competition tasks and finalize adjustments. Prepare for transport and setup.
    \end{itemize}
\end{enumerate}
The schedule ensures a structured development process for a fully tested ROV.

\subsubsection{Resource Management}

\vspace{-0.3\baselineskip}
\begin{itemize}[leftmargin=0pt, itemindent=20pt]
    \setlength{\itemsep}{0pt}
    \item \textbf{Custom vs. Commercial Solutions:} We developed custom ESCs, a USB Hub, a Square Canister, and manipulators for integration, performance, and cost efficiency.
    \item \textbf{Cloud-Based Collaboration:}
    \vspace{-0.5\baselineskip}
    \begin{itemize}
        \setlength{\itemsep}{0pt}
        \item Cloud storage enabled sharing of design files and task submissions for remote collaboration.
        \item Altium shared models ensured access to the latest PCB designs.
    \end{itemize}
\end{itemize}

\subsubsection{Procedures \& Workflow}

\vspace{-0.3\baselineskip}
\begin{itemize}[leftmargin=0pt, itemindent=20pt]
    \setlength{\itemsep}{0pt}
    \item \textbf{Agile Development Approach:}
    \vspace{-0.5\baselineskip}
    \begin{itemize}[leftmargin=35pt, itemindent=0pt]
        \setlength{\itemsep}{0pt}
        \item \textbf{\textit{Agile methodology}} promoted collaboration and modularity.
        \item \textbf{\textit{Notion}} managed sprint planning, tracked tasks, and documented our work.
    \end{itemize}
    \item \textbf{Communication \& Coordination:}
    \vspace{-0.5\baselineskip}
    \begin{itemize}[leftmargin=35pt, itemindent=0pt]
        \setlength{\itemsep}{0pt}
        \item Weekly Online Meetings: Weekly virtual meetings via \textbf{\textit{Discord}} allowed real-time updates.
        \item \textbf{\textit{Miro}} for Visualization: Used for mind maps and flowcharts. 
        \item \textbf{\textit{Overleaf}} for Documentation: Enabled efficient collaboration.
        \item \textbf{\textit{GitHub}} for development: Managed (CI/CD), version control, and issue tracking.
    \end{itemize}
\end{itemize}

\subsubsection{Protocols \& Problem-Solving}
\vspace{-0.5\baselineskip}
\begin{itemize}[leftmargin=0pt, itemindent=20pt]
    \setlength{\itemsep}{0pt}
    \item \textbf{Safety \& Reliability:} Strict testing ensured safe underwater operation.
    \item \textbf{Code \& Hardware Optimization:}
    \vspace{-0.5\baselineskip}
    \begin{itemize}[leftmargin=35pt, itemindent=0pt]
        \setlength{\itemsep}{0pt}
        \item \textbf{\textit{GitHub}} enabled parallel software development and version tracking.
        \item Custom hardware optimized power efficiency.
    \end{itemize}
    \item \textbf{Issue Tracking \& Contingency Planning:}
    \vspace{-0.5\baselineskip}
    \begin{itemize}[leftmargin=35pt, itemindent=0pt]
        \setlength{\itemsep}{0pt}
        \item \textbf{\textit{Notion}} documented technical challenges and solutions.
        \item \textbf{\textit{Miro’s}} visualization tools assisted in analyzing issues.
    \end{itemize}
\end{itemize}

By integrating Agile workflows, cloud-based collaboration, real-time communication, and custom-built hardware, we ensured Kamikaze met its objectives.