\section{Operational Safety Checklist} \label{app:operational_safety_checklist}

\subsection{Pre-Deployment}
\begin{itemize}[label=\ding{111}, leftmargin=0pt, itemindent=15pt]
    \setlength{\itemsep}{0pt}
    \item On deck in proper safety attire.
    \item Ensure power is OFF.
    \item Clear poolside of obstructions.
    \item Confirm untangled tether connected securely with strain relief.
    \item Check tether connection to Control Unit.
    \item Verify no exposed wires or loose connections.
    \item Confirm electronics housing sealing.
    \item Ensure control computer is operational.
\end{itemize}
\subsection{Power Up}
\begin{itemize}[label=\ding{111}, leftmargin=0pt, itemindent=15pt]
    \setlength{\itemsep}{0pt} 
    \item Confirm ROV receives 48V.
    \item Perform dry tests on thrusters, manipulators, and payloads.
    \item Check all video feeds.
\end{itemize}
\subsection{Launch and Water Entry}
\begin{itemize}[label=\ding{111}, leftmargin=0pt, itemindent=15pt]
    \setlength{\itemsep}{0pt}
    \item Two members handle ROV.
    \item Tether handler holds tether.
    \item Visually inspect for leaks and air bubbles.
    \item Test thrusters, manipulators, and payloads.
\end{itemize}
\subsection{Communication Loss}
\begin{itemize}[label=\ding{111}, leftmargin=0pt, itemindent=15pt]
    \setlength{\itemsep}{0pt}
    \item Reboot ROV.
    \item Resend test package.
  
If no communication:
  
    \item Power down ROV.
    \item Retrieve ROV via tether.
    \item Check for damage or leaks.
    \item Dry Test
\end{itemize}
\subsection{Retrieval}
\begin{itemize}[label=\ding{111}, leftmargin=0pt, itemindent=15pt]
    \setlength{\itemsep}{0pt}
    \item Surface ROV and turn off thrusters.
    \item Assigned crew grab ROV by handles.
    \item Secure ROV on deck.
    \item Power down ROV and Control Unit.
\end{itemize}